---
title: "Supplementary Figure 7"
format: html
---

# Blurb

**Supplementary Figure 7: Marker Co-expression for Vğ›¿2 cells at baseline and after activation ex vivo** Manually gated Vğ›¿2 cells across all HIV-unexposed (HU) specimens were concatenated and marker co-expressions matrices were generated using CytoGLMM R package. The heatmap function indicates the extent of marker co-expression, ranging from low (blue) to high (red). (A) Marker co-expression plot for cord blood Vğ›¿2 cells at baseline. (B) Marker co-expression plot of cord blood Vğ›¿2 cells after activation with PMA+ionomycin.

# Code

## Tetramer

```{r}
library(feather)
library(dplyr)
library(CytoGLMM)
library(ggcorrplot)
```

```{r}
StorageLocation <- file.path("SupplementaryFigures", "SupplementaryFigure7")

Location <- file.path("data", "Feather")
TheName <- "ILTsTetramerCtrl"
TheFullName <- paste0(TheName, ".feather")
FeatherOutpath <- file.path(Location, TheFullName)
```

```{r}
Data <- feather::read_feather(FeatherOutpath)
Panel <- read.csv("data/ILTPanelTetramer.csv", check.names = FALSE)
ProteinNames <- c("CD16", "CD27", "CD38", "hCD1d", "hMR1", "CD62L","CD8", "CD69", "CCR4", "Vd2","CD4","CD127", "CD161", "CD45RA", "CD56", "CD7", "IFNg", "CCR6", "NKG2D", "CD25", "PD1", "CD26", "CD3")

Vd2 = Data |> dplyr::filter(celltype == "Vd2")
MAIT = Data |> dplyr::filter(celltype == "MAITs")
NKT = Data |> dplyr::filter(celltype == "NKTs")
```

```{r}
# eval: false
AllNames <- ProteinNames[ProteinNames != "CD3"]
AllNames <- AllNames[AllNames != "CD7"]
AllNames <- AllNames[AllNames != "IFNg"]
AllNames <- AllNames[AllNames != "CD69"]

mcor = cor(Data |> dplyr::select(all_of(AllNames)))
All <- ggcorrplot(mcor, hc.order = TRUE, type = "lower",
           outline.col = "lightgray",
           colors = c("#6D9EC1", "white", "#E46726"))

CorrAll <- All + theme(axis.text.x = element_text(angle = 90, vjust = 1, size=8), axis.text.y = element_text(size=8))
```

```{r}
Vd2Names <- ProteinNames[ProteinNames != "hMR1"]
Vd2Names <- Vd2Names[Vd2Names != "hCD1d"]
Vd2Names <- Vd2Names[Vd2Names != "CD7"]
Vd2Names <- Vd2Names[Vd2Names != "CD3"]
Vd2Names <- Vd2Names[Vd2Names != "Vd2"]
Vd2Names <- Vd2Names[Vd2Names != "CD69"]
Vd2Names <- Vd2Names[Vd2Names != "IFNg"]

mcor = cor(Vd2 |> dplyr::select(all_of(Vd2Names)))
Vd2 <- ggcorrplot(mcor, hc.order = TRUE, type = "lower",
           outline.col = "lightgray",
           colors = c("#6D9EC1", "white", "#E46726"))

CorrVd2 <- Vd2 + theme(axis.text.x = element_text(angle = 90, vjust = 1, size=8), axis.text.y = element_text(size=8))

AssembledName <- paste0("Vd2Correlation", "Tetramer.png")
SendMeOnMyWay <- file.path(StorageLocation, AssembledName)
ggsave(filename = SendMeOnMyWay, CorrVd2, dpi = 600, width = 6, height = 4)
```

## PMA

```{r}
library(feather)
library(dplyr)
library(CytoGLMM)
library(ggcorrplot)
```

```{r}
Location <- file.path("data", "Feather")
TheName <- "ILTsAntibodyPMA"
TheFullName <- paste0(TheName, ".feather")
FeatherOutpath <- file.path(Location, TheFullName)
```

```{r}
Data <- feather::read_feather(FeatherOutpath)
Panel <- read.csv("data/ILTPanelAntibody.csv", check.names = FALSE)
ProteinNames <- c("CD16", "CD27", "CD38", "hCD1d", "hMR1", "CD62L","CD8", "CD69", "CCR4", "Vd2","CD4","CD127", "CD161", "CD45RA", "CD56", "CD7", "CD69", "TNFa", "IFNg", "CCR6", "NKG2D", "CD25", "PD1", "CD26", "CD3")

Vd2 = Data |> dplyr::filter(celltype == "Vd2")
MAIT = Data |> dplyr::filter(celltype == "MAITs")
NKT = Data |> dplyr::filter(celltype == "NKTs")
```

```{r}
# eval: false
AllNames <- ProteinNames[ProteinNames != "CD16"]

mcor = cor(Data |> dplyr::select(all_of(AllNames)))
All <- ggcorrplot(mcor, hc.order = TRUE, type = "lower",
           outline.col = "lightgray",
           colors = c("#6D9EC1", "white", "#E46726"))

CorrAll <- All + theme(axis.text.x = element_text(angle = 90, vjust = 1, size=8), axis.text.y = element_text(size=8))
```

```{r}
Vd2Names <- ProteinNames[ProteinNames != "hMR1"]
Vd2Names <- Vd2Names[Vd2Names != "hCD1d"]
Vd2Names <- Vd2Names[Vd2Names != "CD7"]
Vd2Names <- Vd2Names[Vd2Names != "CD3"]
Vd2Names <- Vd2Names[Vd2Names != "Vd2"]
Vd2Names <- Vd2Names[Vd2Names != "CD69"]
Vd2Names <- Vd2Names[Vd2Names != "CD16"]

mcor = cor(Vd2 |> dplyr::select(all_of(Vd2Names)))
Vd2 <- ggcorrplot(mcor, hc.order = TRUE, type = "lower",
           outline.col = "lightgray",
           colors = c("#6D9EC1", "white", "#E46726"))

CorrVd2 <- Vd2 + theme(axis.text.x = element_text(angle = 90, vjust = 1, size=8), axis.text.y = element_text(size=8))

AssembledName <- paste0("Vd2Correlation", "PMAAntibody.png")
SendMeOnMyWay <- file.path(StorageLocation, AssembledName)
ggsave(filename = SendMeOnMyWay, CorrVd2, dpi = 600, width = 6, height = 4)
```

```{r}
print("GoodBye")
```
