---
title: "Figure 4"
format: docx
---

# Blurb

**Figure 4: Altered marker expression of cord blood ILT subsets in HEU infants.** The beeswarm plots compare the expression of specific markers between exposure groups. Symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify HIV-exposure status. (A) Proportions of CD62L+ (left), CD161+ (center), and CD56+ (right) cells in the DN V𝛿2 cluster. (B) Proportions of CD62L+ cells in the V𝛿2 T17 cluster. (C) Proportions of CD161+ cells in the NKT PaCMAP cluster.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

## DN Vd2

```{r}
StorageLocation <- file.path("MainFigures/Figure4")
data <- read.csv("data/Vd2DN_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure C.I

```{r}
PlotName <- "Vd2DN_TetLocal_CD62L"

ThePlot <- map(names(data)[16], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
   statsHeight=0.4, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.II

```{r}
PlotName <- "Vd2DN_TetLocal_CD161"

ThePlot <- map(names(data)[24], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
   statsHeight=0.8, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.III

```{r}
PlotName <- "Vd2DN_TetLocal_CD56"

ThePlot <- map(names(data)[26], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
   statsHeight=0.1, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + 
    theme(plot.caption = element_blank(), 
    axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## T17 Vd2

```{r}
StorageLocation <- file.path("MainFigures/Figure4")
data <- read.csv("data/Vd2T17_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure B.I

```{r}
PlotName <- "Vd2T17_TetLocal_CD62L"

ThePlot <- map(names(data)[16], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, 
  statsHeight=0.15, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(), 
     axis.text.y = element_text(size = 15),
      axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## NKTs

```{r}
StorageLocation <- file.path("MainFigures/Figure4")
data <- read.csv("data/NKT_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure C.I

```{r}
PlotName <- "NKT_TetLocal_CD161"

ThePlot <- map(names(data)[24], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
   statsHeight=1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## NKT CD56

```{r}
PlotName <- "NKT_TetLocal_CD56"

ThePlot <- map(names(data)[26], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 0.7,
  statsHeight=0.1, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

#ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

# Epilogue

```{r}
print("Goodbye")
```