---
title: "Supplementary Figure 9"
format: docx
---

# Blurb

**Supplementary Figure 9: Altered global marker expression in neonatal HEU ILT subsets.** The beeswarm plots compare the expression of specific markers between exposure groups. Symbols show individual values, boxplots show median with IQR, and whiskers showing the +/- 1.5 IQR range. Shape and color identify HIV-exposure status. (A) Baseline proportion of CD56 expression for MAITs identified by antibody (CD161^hi^ V⍺7.2+, left) or tetramer (CD161^hi^ hMR1 5-OP-RU+, right) staining. (B) Baseline proportion of total CD62L expression for NKTs identified by antibody (V⍺24J⍺18+, left) or tetramer (hCD1d PBS-57+, right) staining. (C) Frequency of CCR6+ V𝛿2 cells after activation with PMA+ionomycin.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

## MAITs

### Figure A.I

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure9")
data <- read.csv("data/ILT_CtrlTetramer_MAITExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "MAIT_CD56_Tetramer"

ThePlot <- map(names(data)[20], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statsHeight=0.55, scalePercent=TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.II

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure9")
data <- read.csv("data/ILT_CtrlAntibody_MAITExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "MAIT_CD56_Antibody"

ThePlot <- map(names(data)[20], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statsHeight=0.55, scalePercent=TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## NKTs

### Figure B.I

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure9")
data <- read.csv("data/ILT_CtrlTetramer_NKTExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "NKT_CD62L_Tetramer"

ThePlot <- map(names(data)[22], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statsHeight=0.5, scalePercent=TRUE,
   correction = "BH", keepNS=FALSE, showClose=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0, NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure B.II

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure9")
data <- read.csv("data/ILT_CtrlAntibody_NKTExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "NKT_CD62L_Antibody"

ThePlot <- map(names(data)[22], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statsHeight=0.5, scalePercent=TRUE, correction = "BH", showClose=FALSE, 
  keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0, NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure9")
data <- read.csv("data/ILT_PMAAntibody_Vd2ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "Vd2_CCR6_PMAAntibody"

ThePlot <- map(names(data)[17], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statsHeight=0.5, scalePercent=TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

```{r}
print("Goodbye")
```