---
title: "Figure 8"
format: docx
---

# Blurb

**Figure 8: Altered cytokine expression of cord blood ILT subsets in HEU infants after activation.** The beeswarm plots compare the expression of specific markers between exposure groups. The symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify HIV-exposure status. (A) Proportion of TNFâº+ (left) and IFNğ›¾+ (middle) cells in Vğ›¿2 DN cluster. (B) Proportion of CD69+ cells in the Vğ›¿2 PD1hi cluster.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

```{r}
StorageLocation <- file.path("MainFigures/Figure8")
```

# Vd2 CD4

```{r}
data <- read.csv("data/Vd2CD4_PMAAbIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure A.I

```{r}
PlotName <- "Vd2CD4_PMALocal_CD69"

ThePlot <- map(names(data)[17], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype", 
normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
 cex = 2, size = 3, corral.width = 1, statLines = TRUE, statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.II

```{r}
PlotName <- "Vd2CD4_PMALocal_CD107a"

ThePlot <- map(names(data)[13], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
  statLines = TRUE, statsHeight = 0.1, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## CD8 Vd2

```{r}
data <- read.csv("data/Vd2CD8_PMAAbIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure B.I

```{r}
PlotName <- "Vd2CD8_PMALocal_CD25"

ThePlot <- map(names(data)[32], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
   statLines = TRUE, statsHeight = 0.2, scalePercent = TRUE, correction = "BH", keepNS=FALSE))
  
Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## DN Vd2

```{r}
data <- read.csv("data/Vd2DN_PMAAbIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure C.I

```{r}
PlotName <- "Vd2DN_PMALocal_CD69"

ThePlot <- map(names(data)[17], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
  statLines = TRUE, statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))
  
Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.II

```{r}
PlotName <- "Vd2DN_PMALocal_TNFa"

ThePlot <- map(names(data)[33], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
   statLines = TRUE, statsHeight = 1.0, showClose=FALSE, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.III

```{r}
PlotName <- "Vd2DN_PMALocal_IFNg"

ThePlot <- map(names(data)[28], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
  statLines = TRUE, statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))
  

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.IV

```{r}
PlotName <- "Vd2DN_PMALocal_NKG2D"

ThePlot <- map(names(data)[31], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, 
  statLines = TRUE, statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## T17 Vd2

```{r}
data <- read.csv("data/Vd2T17_PMAAbIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure D.I

```{r}
PlotName <- "Vd2T17_PMALocal_CCR6"

ThePlot <- map(names(data)[29], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
  statLines = TRUE, statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
    axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure D.II

```{r}
PlotName <- "Vd2T17_PMALocal_CD107a"

ThePlot <- map(names(data)[13], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
  statLines = TRUE, statsHeight = 0.1, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
    axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## PD1hi Vd2

```{r}
data <- read.csv("data/Vd2PD1_PMAAbIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure E.I

```{r}
PlotName <- "Vd2PD1_PMALocal_CD69"

ThePlot <- map(names(data)[17], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1,
  statLines = TRUE, statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(
    plot.caption = element_blank(), axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

# Epilogue

```{r}
print("Goodbye")
```