---
title: "Supplementary Figure 15"
format: docx
---

# Blurb

**Supplementary Figure 15: Sex-based differences in ILT marker expression after polyclonal stimulation.** (A) The beeswarm plots show the proportions of cells expressing individual markers listed on the x-axis for V𝛿2 (A), MAIT (B) and NKT (C) cells, respectively. The symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify infant sex.

# Code

```{r}
StorageLocation <- file.path("SupplementaryFigures", "SupplementaryFigure15")
panel <- file.path("data", "ILTPanelAntibody.csv")
```

```{r}
#| code-fold: true
library(Coereba)

shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

```{r}
XAxisLevels <- c("CD8", "CD4", "CD26", "CCR6", "CD161", "NKG2D", "CD27", "CD45RA",
                 "CD127", "CCR4", "CD25", "PD1", "CD38", "CD69", "TNFa", "IFNg", "CD107a")
```

## Figure A

```{r}
File <- file.path("data", "ILT_PMAAntibody_Vd2ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)
data$ptype <- factor(data$ptype, levels=c("Female", "Male"))

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="infant_sex", shape_palette = shape_sex,
                            fill_palette = fill_sex, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="Vd2_PMAAntibody_sex", corral.width=0.6,
                            style="individual", width=12)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("Vd2_PMAAntibody_sex.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

## Figure B

```{r}
File <- file.path("data", "ILT_PMAAntibody_MAITExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)
data$ptype <- factor(data$ptype, levels=c("Female", "Male"))

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="infant_sex", shape_palette = shape_sex,
                            fill_palette = fill_sex, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="MAIT_PMAAntibody_sex", corral.width=0.6,
                            style="individual", width=12)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("MAIT_PMAAntibody_sex.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

## Figure C

```{r}
File <- file.path("data", "ILT_PMAAntibody_NKTExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)
data$ptype <- factor(data$ptype, levels=c("Female", "Male"))

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="infant_sex", shape_palette = shape_sex,
                            fill_palette = fill_sex, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="NKT_PMAAntibody_sex", corral.width=0.6,
                            style="individual", width=12)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("NKT_PMAAntibody_sex.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

```{r}
print("Goodbye")
```