---
title: "Supplemental Figure 3"
format: docx
---

# Blurb

**Supplemental Figure 3: Antibody and Tetramer-staining frequency of ILT subsets in HEU infants.** The beeswarm plots show the frequency of ILT subsets with individual symbols representing unique specimens, boxplots depicting median and IQR, with whiskers showing the +/- 1.5 IQR range. (A) Frequency of MAITs identified by antibody (CD161^hi^ V⍺7.2+, left) or tetramer (CD161^hi^ hMR1 5-OP-RU+, right). (B) Frequency of MAITs identified by antibody (CD161^hi^ V⍺7.2+, left) or tetramer (CD161^hi^ hMR1 5-OP-RU+, right) and pooled by HIV-exposure. (C) Frequency of NKTs identified by antibody (V⍺24J⍺18+, left) or tetramer (hCD1d PBS-57+, right) staining. (D) Frequency of NKTs pooled by identified by antibody (V⍺24J⍺18+, left) or tetramer (hCD1d PBS-57+, right) staining and pooled by HIV-exposure.

# Code

```{r}
library(Coereba)
library(dplyr)
library(purrr)
library(ggplot2)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

```{r}
StorageLocation <- file.path("SupplementaryFigures", "SupplementaryFigure3")

AntibodyData <- read.csv("data/SFC_Ctrl_Antibody_Freq.csv", check.names=FALSE)
AntibodyData$ptype <- factor(AntibodyData$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
AntibodyData <- AntibodyData |> mutate(
    ART = case_when(
      ptype == "HU" ~ "HU",
      ptype == "HEU-lo" ~ "HEU",
      ptype == "HEU-hi" ~ "HEU",
      TRUE ~ NA_character_
    )
  )
AntibodyData$ART <- factor(AntibodyData$ART, levels=c("HU", "HEU"))

TetramerData <- read.csv("data/SFC_Ctrl_Tetramer_Freq.csv", check.names=FALSE)
TetramerData$ptype <- factor(TetramerData$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
TetramerData <- TetramerData |> mutate(
    ART = case_when(
      ptype == "HU" ~ "HU",
      ptype == "HEU-lo" ~ "HEU",
      ptype == "HEU-hi" ~ "HEU",
      TRUE ~ NA_character_
    )
  )
TetramerData$ART <- factor(TetramerData$ART, levels=c("HU", "HEU"))
```

## Figure A.I

```{r}
data <- AntibodyData
PlotName <- "MAITFreqAntibody"

ThePlot <- map(names(data)[10], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, statsHeight=0.25, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) + lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure A.II

```{r}
data <- TetramerData
PlotName <- "MAITFreqTetramer"

ThePlot <- map(names(data)[10], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, statLines=TRUE, statsHeight=0.3, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure B.I

```{r}
data <- AntibodyData
PlotName <- "MAITFreqAntibody"

ThePlot <- map(names(data)[10], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ART", normality = "dagostino", shape_palette = shape_art, fill_palette = fill_art, cex = 2, size = 3, corral.width = 1, statLine = TRUE, statsHeight=0.25, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) + lims(y=c(0,NA))

Plot <- Plot + scale_x_discrete(labels=c("HU"="HU", "HEU"="All HEU"))

Abbreviation <- "_Pooled.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure B.II

```{r}
data <- TetramerData
PlotName <- "MAITFreqTetramer"

ThePlot <- map(names(data)[10], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ART", normality = "dagostino", shape_palette = shape_art, fill_palette = fill_art, cex = 2, size = 3, corral.width = 1, statLine = TRUE, statsHeight=0.3, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot <- Plot + scale_x_discrete(labels=c("HU"="HU", "HEU"="All HEU"))

Plot

Abbreviation <- "_Pooled.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure C.I

```{r}
data <- AntibodyData
PlotName <- "NKTFreqAntibody"

ThePlot <- map(names(data)[11], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, statsHeight=0.3, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure C.II

```{r}
data <- TetramerData
PlotName <- "NKTFreqTetramer"

ThePlot <- map(names(data)[11], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, statsHeight=0.3, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure D.I

```{r}
data <- AntibodyData
PlotName <- "NKTFreqAntibody"

ThePlot <- map(names(data)[11], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ART", normality = "dagostino", shape_palette = shape_art, fill_palette = fill_art, cex = 2, size = 3, corral.width = 1, statLine = TRUE, statsHeight=0.3, correction = "BH", keepNS=FALSE, showClose = FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot <- Plot + scale_x_discrete(labels=c("HU"="HU", "HEU"="All HEU"))

Plot

Abbreviation <- "_Pooled.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure D.II

```{r}
data <- TetramerData
PlotName <- "NKTFreqTetramer"

ThePlot <- map(names(data)[11], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ART", normality = "dagostino", shape_palette = shape_art, fill_palette = fill_art, cex = 2, size = 3, corral.width = 1, statLine = TRUE, statsHeight=0.3, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) + lims(y=c(0,NA))

Plot <- Plot + scale_x_discrete(labels=c("HU"="HU", "HEU"="All HEU"))

Plot

Abbreviation <- "_Pooled.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure E.I

```{r}
data <- AntibodyData
PlotName <- "Vd2FreqAntibody"

ThePlot <- map(names(data)[12], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype, cex = 2, size = 3, corral.width = 1, statsHeight=2.5, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + theme(plot.caption = element_blank(), axis.text.y = element_text(size = 15), axis.text.x= element_text(size = 15)) + lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure E.II

```{r}
print("Goodbye")
```