---
title: "Figure 6"
format: docx
---

# Blurb

**Figure 6: Marker expression of V𝛿2 T cells after in vitro expansion by culture condition.** V𝛿2 T cells were stimulated in vitro with ZOL+IL-2, BCG+IL-2, or IL-2 alone and expanded in culture for 17 days. (A) The heatmap summarizes marker expression of V𝛿2 T cells by culture condition at day 17. The 50th percentile of the distribution of median frequencies of cells positive for each marker is displayed by a combination of colors and symbols. (B) The beeswarm plots compare the expression of specific markers between exposure groups 17 days after ZOL stimulation, showing individual values, median and IQR, with whiskers showing the +/- 1.5 IQR range for NKG2D+ (left) and CD28+ (right) V𝛿2 T cells.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
library(gt)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

```{r}
StorageLocation <- file.path("MainFigures", "Figure6")
```

## Figure A

```{r}
File <- file.path("data", "gd_D17Phenotype_HeatmapData.csv")
data <- read.csv(File, check.names=FALSE)

RemoveMarkers <- c("CD3", "Vd1", "Vd2")
MarkerOrder <- c("CD45RA", "CD27", "PD1", "CD56", "CD16", "NKG2D", "NKG2A", "Perforin", "CD28", "CD25")

Table <- Coereba:::Coereba_Heatmap(data=data, RemoveMarkers=RemoveMarkers, MarkerOrder=MarkerOrder)
```

```{r}
Greeked <- Table |>
  sub_values(pattern="Vd2", replacement = "V\u03B42") |>
  sub_values(pattern="TNFa", replacement = "TNF\u03B1") |> 
  sub_values(pattern="IFNg", replacement = "IFN\u03B3") |>
  sub_values(pattern="Va7.2", replacement = "V\u03B17.2") |> 
  sub_values(pattern="Va24Ja18", replacement = "V\u03B124J\u03B118")

Greeked <- Greeked |> opt_table_outline(style="solid", width=px(2), color="black") |>
  tab_options(column_labels.border.top.style = "solid", column_labels.border.top.width = px(2),
              column_labels.border.top.color = "black", table.border.bottom.style = "double",
              table.border.bottom.width = px(2), table.border.bottom.color = "black", 
              table.font.size = 22)
```

```{r}
filename <- "D17_Phenotype.png"
StorageLocation1 <- file.path(StorageLocation, filename)
Greeked |> gtsave(StorageLocation1, vwidth = 1500, vheight = 1000)
```

## Figure B.I

```{r}
data <- read.csv("data/D17P1ZOL_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "D17P1_ZOL_CD28"

ThePlot <- map(names(data)[14], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statLines=TRUE,
   statsHeight = 0.8, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
   theme(plot.caption = element_blank(),
    axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure B.II

```{r}
data <- read.csv("data/D17P2ZOL_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "D17P2_ZOL_NKG2D"

ThePlot <- map(names(data)[14], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statLines=TRUE,
  statsHeight = 1.0, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
   theme(plot.caption = element_blank(),
   axis.text.y = element_text(size = 15),
   axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure B.III

```{r}
PlotName <- "D17P2_ZOL_NKG2A"

ThePlot <- map(names(data)[15], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "ptype", normality = "dagostino", shape_palette = shape_ptype,
  fill_palette = fill_ptype, cex = 2, size = 3, statLines=TRUE,
  statsHeight = 0.5, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
   theme(plot.caption = element_blank(),
    axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

```{r}
print("Goodbye")
```

# Part II original blurb

**Figure 6b: Lower cytokine production following restimulation in HEU infants.** Expanded V𝛿2 T cells were restimulated with plate-bound ⍺-𝛾𝛿 TCR antibody after 17-days in culture. (A) The heatmap summarizes cytokine production and degranulation of V𝛿2 T cells by culture condition. The 50th percentile of the distribution of median frequencies of cells positive for each marker is displayed by a combination of colors and symbols. (B) The beeswarm plots compare between exposure groups the cytokine production by BCG-expanded V𝛿2 T cells in response to restimulation for the frequency of TNF⍺+ (upper), IFN𝛾+(middle), and polyfunctional TNF⍺+ IFN𝛾+ (lower). The symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify HIV-exposure status.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
library(gt)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

## Figure C

```{r}
StorageLocation <- file.path("MainFigures/Figure6")
data <- read.csv("data/gd_D17Cytokine_HeatmapData.csv")

RemoveMarkers <- c("Vd2")
MarkerOrder <- c("CD45RO", "CD27", "PD1", "CD56", "TNFa", "IFNg", "CD107a")

Table <- Coereba:::Coereba_Heatmap(data=data, RemoveMarkers=RemoveMarkers, MarkerOrder=MarkerOrder)
```

```{r}
Greeked <- Table |>
  sub_values(pattern="Vd2", replacement = "V\u03B42") |>
  sub_values(pattern="TNFa", replacement = "TNF\u03B1") |> 
  sub_values(pattern="IFNg", replacement = "IFN\u03B3") |>
  sub_values(pattern="Va7.2", replacement = "V\u03B17.2") |> 
  sub_values(pattern="Va24Ja18", replacement = "V\u03B124J\u03B118")

Greeked <- Greeked |> opt_table_outline(style="solid", width=px(2), color="black") |>
  tab_options(column_labels.border.top.style = "solid", column_labels.border.top.width = px(2),
              column_labels.border.top.color = "black", table.border.bottom.style = "double",
              table.border.bottom.width = px(2), table.border.bottom.color = "black", 
              table.font.size = 22)
```

```{r}
filename <- "D17_Cytokine.png"
StorageLocation <- file.path(StorageLocation, filename)
Greeked |> gtsave(StorageLocation, vwidth = 1500, vheight = 1000)
```

## Figure D.I

```{r}
StorageLocation <- file.path("MainFigures/Figure10")
data <- read.csv("data/D17CKBCG_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))

data <- data %>% dplyr::filter(!bid %in% "INF182") # Quality Disqual
```

```{r}
PlotName <- "D17CK_BCG_TNFa"

ThePlot <- map(names(data)[14], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 2, size = 3, corral.width = 1, statLines = TRUE, statsHeight=0.8, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
   theme(plot.caption = element_blank(),
    axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure D.II

```{r}
PlotName <- "D17CK_BCG_IFNg"

ThePlot <- map(names(data)[15], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 2, size = 3, corral.width = 1, statLines = TRUE, statsHeight=0.8, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
   theme(plot.caption = element_blank(),
    axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## Figure D.III

```{r}
StorageLocation <- file.path("MainFigures/Figure10")
data <- read.csv("data/CytokinesD17.csv", check.names=FALSE)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))

data <- data %>% dplyr::filter(!bid %in% "INF182") # Quality Disqual
data
```

```{r}
PlotName <- "D17CK_BCG_TNFaIFNg"

ThePlot <- map(names(data)[10], ~ Utility_Behemoth(data = data, var = .x, myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 2, size = 3, corral.width = 1, statLines = TRUE, statsHeight=0.8, scalePercent = TRUE, correction = "BH", keepNS=FALSE))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
   theme(plot.caption = element_blank(),
    axis.text.y = element_text(size = 15),
     axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

```{r}
print("Goodbye")
```