---
title: "Figure 7"
format: docx
---

# Blurb

**Figure 7: Semi-supervised analysis highlights cord blood V𝛿2 T cell functional heterogeneity between clusters after polyclonal stimulation** The beeswarm plots on the left show the proportion of cells in each V𝛿2 PaCMAP cluster (from Figure 5.C) comparing the three exposure groups. The beeswarm plots on the right display the proportion of V𝛿2 T cells in the respective cluster expressing the individual markers listed on the x-axis. The symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify HIV-exposure status. (A) depicts results for the CD4+ PaCMAP cluster, (B) for CD8+, (C) for DN, (D) for T17, and (E) for PD1hi respectively.

# Code

```{r}
StorageLocation <- file.path("MainFigures", "Figure7")
panel <- file.path("data", "ILTPanelAntibody.csv")
```

```{r}
#| code-fold: true
library(Coereba)
library(ggplot2)

shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

```{r}
XAxisLevels <- c("CD8", "CD4", "CD26", "CCR6", "CD161", "NKG2D", "CD27", "CD45RA",
                 "CD127", "CCR4", "CD25", "PD1", "CD38", "CD69", "TNFa", "IFNg", "CD107a")
```

## Figure A.I

```{r}
PlotName <- "Vd2CD4_ptype_Freq"

data <- read.csv("data/SubsetFrequenciesPMA.csv", check.names=FALSE)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
TheSubset <- data |> dplyr::filter(Population %in% "Vd2_CD4")

Plot <- Utility_Behemoth(data = TheSubset, var = "PopFreq", myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 3, size = 3, corral.width = 4, statLines = FALSE, statsHeight = 0.8, scalePercent = TRUE, correction = "BH")

ThePlot <- Plot + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

ThePlot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, ThePlot, dpi = 600, width = 4, height = 3)
```

## Figure A.II

```{r}
File <- file.path("data", "Vd2CD4_PMAAbIsland_ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:36]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="Vd2CD4_PMAAntibody_Ptype", corral.width=0.8)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("Vd2CD4_PMAAntibody_Ptype.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

## Figure B.I

```{r}
PlotName <- "Vd2CD8_ptype_Freq"

data <- read.csv("data/SubsetFrequenciesPMA.csv", check.names=FALSE)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
TheSubset <- data |> dplyr::filter(Population %in% "Vd2_CD8")

Plot <- Utility_Behemoth(data = TheSubset, var = "PopFreq", myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 3, size = 3, corral.width = 4, statLines = FALSE, statsHeight = 0.8, scalePercent = TRUE, correction = "BH")

ThePlot <- Plot + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

ThePlot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, ThePlot, dpi = 600, width = 4, height = 3)
```

## Figure B.II

```{r}
File <- file.path("data", "Vd2CD8_PMAAbIsland_ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:36]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="Vd2CD8_PMAAntibody_Ptype", corral.width=0.8)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("Vd2CD8_PMAAntibody_Ptype.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

## Figure C.I

```{r}
PlotName <- "Vd2DN_ptype_Freq"

data <- read.csv("data/SubsetFrequenciesPMA.csv", check.names=FALSE)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
TheSubset <- data |> dplyr::filter(Population %in% "Vd2_DN")

Plot <- Utility_Behemoth(data = TheSubset, var = "PopFreq", myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 3, size = 3, corral.width = 4, statLines = FALSE, statsHeight = 0.8, scalePercent = TRUE, correction = "BH")

ThePlot <- Plot + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

ThePlot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, ThePlot, dpi = 600, width = 4, height = 3)
```

## Figure C.II

```{r}
File <- file.path("data", "Vd2DN_PMAAbIsland_ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:36]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="Vd2DN_PMAAntibody_Ptype", corral.width=0.8)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("Vd2DN_PMAAntibody_Ptype.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

## Figure D.I

```{r}
PlotName <- "Vd2T17_ptype_Freq"

data <- read.csv("data/SubsetFrequenciesPMA.csv", check.names=FALSE)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
TheSubset <- data |> dplyr::filter(Population %in% "Vd2_T17")

Plot <- Utility_Behemoth(data = TheSubset, var = "PopFreq", myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 3, size = 3, corral.width = 4, statLines = TRUE, statsHeight = 0.8, scalePercent = TRUE,
  correction = "BH", keepNS=FALSE)

ThePlot <- Plot + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

ThePlot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, ThePlot, dpi = 600, width = 4, height = 3)
```

## Figure D.II

```{r}
File <- file.path("data", "Vd2T17_PMAAbIsland_ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:36]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="Vd2T17_PMAAntibody_Ptype", corral.width=0.8)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("Vd2T17_PMAAntibody_Ptype.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

## Figure E.I

```{r}
PlotName <- "Vd2PD1_ptype_Freq"

data <- read.csv("data/SubsetFrequenciesPMA.csv", check.names=FALSE)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
TheSubset <- data |> dplyr::filter(Population %in% "Vd2_PD1")

Plot <- Utility_Behemoth(data = TheSubset, var = "PopFreq", myfactor = "ptype",
 normality = "dagostino", shape_palette = shape_ptype, fill_palette = fill_ptype,
  cex = 3, size = 3, corral.width = 0.5, statLines = FALSE, statsHeight = 0.8, scalePercent = TRUE, correction = "BH")

ThePlot <- Plot + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

ThePlot

Abbreviation <- "_ptype.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, ThePlot, dpi = 600, width = 4, height = 3)
```

## Figure E.II

```{r}
File <- file.path("data", "Vd2PD1_PMAAbIsland_ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:36]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=FALSE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="Vd2PD1_PMAAntibody_Ptype", corral.width=0.8)

ThePlot <- Plot + scale_x_discrete(labels = function(y) {
    ifelse(y == "IFNg", expression(IFN * gamma),
           ifelse(y == "TNFa", expression(TNF * alpha),
                                       as.character(y)))
  })

TheFileName <- paste0("Vd2PD1_PMAAntibody_Ptype.png")
SendMeOnMyWay <- file.path(StorageLocation, TheFileName)
ggsave(filename = SendMeOnMyWay, ThePlot, dpi = 600, width = 9, height = 3)
```

```{r}
print("Goodbye")
```