---
title: "Figure 7"
format: docx
---

# Blurb

**Figure 7: Altered global marker expression in ILT subsets by infant sex.** The beeswarm plots show the differentially expressed markers in V𝛿2 T cells (A), and in MAIT cells (B). The symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify HIV-exposure status. Shape and color identify infant sex.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

## Vd2

```{r}
StorageLocation <- file.path("MainFigures/Figure11")
data <- read.csv("data/ILT_CtrlTetramer_Vd2ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure A.I NKG2D by Sex

```{r}
PlotName <- "Vd2_NKG2D"

ThePlot <- map(names(data)[19], ~ Utility_Behemoth(data = data, var = .x, myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex, fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.II CD8 by Sex

```{r}
PlotName <- "Vd2Global_CD8"

ThePlot <- map(names(data)[14], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino",
 shape_palette = shape_sex, fill_palette = fill_sex, cex = 2, size = 3,
 statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.III

```{r}
PlotName <- "Vd2_CD45RA"

ThePlot <- map(names(data)[25], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(), 
     axis.text.y = element_text(size = 15),
      axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.IV

```{r}
PlotName <- "Vd2_CD62L"

ThePlot <- map(names(data)[22], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=0.4, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.V

```{r}
PlotName <- "Vd2_CD25"

ThePlot <- map(names(data)[28], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure A.VI

```{r}
PlotName <- "Vd2_CD127"

ThePlot <- map(names(data)[26], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## MAITs

```{r}
StorageLocation <- file.path("MainFigures/Figure11")
data <- read.csv("data/ILT_CtrlTetramer_MAITExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure B.I

```{r}
PlotName <- "MAIT_PD1"

ThePlot <- map(names(data)[29], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## NKTs

```{r}
StorageLocation <- file.path("MainFigures/Figure11")
data <- read.csv("data/ILT_CtrlTetramer_NKTExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure C.I

```{r}
PlotName <- "NKT_NKG2D"

ThePlot <- map(names(data)[19], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) + 
    theme(plot.caption = element_blank(),
     axis.text.y = element_text(size = 15),
      axis.text.x= element_text(size = 15)) #+ lims(y=c(0, NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.II

```{r}
PlotName <- "NKT_CD25"

ThePlot <- map(names(data)[28], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(), 
     axis.text.y = element_text(size = 15),
      axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

```{r}
print("Goodbye")
```