---
title: "Supplementary Figure 8"
format: docx
---

# Blurb

**Supplementary Figure 8: Cord blood ILT subsets at baseline are characterized by specific marker expression profiles.** (A) The beeswarm plots show the proportion of cells expressing individual markers listed on the x-axis for V𝛿2 T (A), MAIT (B) and NKT (C) cells, respectively. The symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify HIV-exposure status.

# Code

```{r}
StorageLocation <- file.path("SupplementaryFigures", "SupplementaryFigure8")
panel <- file.path("data", "ILTPanelTetramer.csv")
```

```{r}
#| code-fold: true
library(Coereba)

shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

```{r}
XAxisLevels <- c("CD8", "CD4", "CD26", "CCR6", "CD161", "CD56", "NKG2D", "CD16", "CD27", "CD45RA", "CD62L", 
                 "CD127", "CCR4", "CD25", "PD1", "CD38")
```

## Figure A

```{r}
File <- file.path("data", "ILT_CtrlTetramer_Vd2ExpressionData.csv")
data <- read.csv(File, check.names=FALSE)

# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:35]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", 
  shape_palette = shape_ptype, fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=TRUE, filterForThese = XAxisLevels, outpath=StorageLocation,
  filename="Vd2_Tetramer_Ptype_2", corral.width=0.4,
  style="individual", width=12)
```

## Figure B

```{r}
File <- file.path("data", "ILT_CtrlTetramer_MAITExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:35]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=TRUE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="MAIT_Tetramer_Ptype", corral.width=0.4,
                            style="individual", width=12)
```

## Figure C

```{r}
File <- file.path("data", "ILT_CtrlTetramer_NKTExpressionData.csv")
data <- read.csv(File, check.names=FALSE)
# CCR7 staining was not up to par for unsupervised analysis, removing from ME plots. 
data <- data |> dplyr::select(-CCR7)
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))

SummaryStats <- data |> dplyr::mutate(Comparison = "Control") |> dplyr::relocate(Comparison, .after="isc_artreg")
Summaries <- purrr::map_dfr(colnames(SummaryStats[10:35]), ~ Utility_Stats(data = SummaryStats,var = .x, myfactor = "Comparison",
  normality = "dagostino", correction = "BH", returnType = "median"))
# View(Summaries)

Plot <- Utility_MarkerPlots(data=data, panel=panel, myfactor="ptype", shape_palette = shape_ptype,
                            fill_palette = fill_ptype, XAxisLevels = XAxisLevels, savePlot=TRUE,
                            filterForThese = XAxisLevels, outpath=StorageLocation,
                            filename="NKT_Tetramer_Ptype", corral.width=0.4,
                            style="individual", width=12)
```

```{r}
print("Goodbye")
```