---
title: "Supplementary Figure 13"
format: docx
---

# Blurb

**Supplementary Figure 13: Sex-based differences in ILT marker expression.** (A) The beeswarm plots display the frequency of differentially expressed markers in the ILT clusters identified in Figure 1.C. Symbols show individual values, boxplots show median and IQR, with whiskers indicating the +/- 1.5 IQR range. Shape and color identify infant sex. (A) displays differential PD1 expression in MAITS, (B) differential NKG2D expression in NKTs, (C), (D), and (E) depict differentially expressed markers in CD4+, CD8+ and CD4-CD8- (DN) V𝛿2 cell clusters respectively.

# Code

```{r}
library(purrr)
library(Coereba)
library(ggplot2)
```

```{r}
#| code-fold: true
shape_sex <- c("Female" = 22, "Male" = 21)
fill_sex <- c("Female" = "white", "Male" = "black")

shape_ptype <- c("HU" = 22, "HEU-lo" = 21, "HEU-hi" = 21)
fill_ptype <- c("HU" = "white", "HEU-lo" = "darkgray", "HEU-hi" = "black")

shape_art <- c("HU" = 22, "HEU" = 21)
fill_art <- c("HU" = "white", "HEU" = "black")

shape_viral <- c("NoViral" = 22, "Viral" = 21)
fill_viral <- c("NoViral" = "white", "Viral" = "black")
```

## MAITs

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure13")
data <- read.csv("data/MAIT_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure A

```{r}
PlotName <- "MAIT_TetLocal_PD1"

ThePlot <- map(names(data)[34], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## NKTs

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure13")
data <- read.csv("data/NKT_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

```{r}
PlotName <- "NKT_TetLocal_NKG2D"

ThePlot <- map(names(data)[31], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure B

## CD4 Vd2s

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure13")
data <- read.csv("data/Vd2CD4_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure C.I

```{r}
PlotName <- "Vd2CD4_TetLocal_NKG2D"

ThePlot <- map(names(data)[31], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure C.II

```{r}
PlotName <- "Vd2CD4_TetLocal_PD1"

ThePlot <- map(names(data)[34], ~ Utility_Behemoth(data = data, var = .x, 
myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
 fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1,statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## DN Vd2s

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure13")
data <- read.csv("data/Vd2DN_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure D.I

```{r}
PlotName <- "Vd2DN_TetLocal_NKG2D"

ThePlot <- map(names(data)[31], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure D.II

```{r}
PlotName <- "Vd2DN_TetLocal_PD1"

ThePlot <- map(names(data)[34], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure D.III

```{r}
PlotName <- "Vd2DN_TetLocal_CD62L"

ThePlot <- map(names(data)[16], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

## CD8 Vd2s

```{r}
StorageLocation <- file.path("SupplementalFigures/SupplementalFigure13")
data <- read.csv("data/Vd2CD8_TetIsland_ExpressionData.csv")
data$ptype <- factor(data$ptype, levels=c("HU", "HEU-lo", "HEU-hi"))
data$infant_sex <- factor(data$infant_sex, levels=c("Female", "Male"))
```

### Figure E.I

```{r}
PlotName <- "Vd2CD8_TetLocal_CD38"

ThePlot <- map(names(data)[12], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=1, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15), 
      axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure E.II

```{r}
PlotName <- "Vd2CD8_TetLocal_CD56"

ThePlot <- map(names(data)[26], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

### Figure E.III

```{r}
PlotName <- "Vd2CD8_TetLocal_CD62L"

ThePlot <- map(names(data)[16], ~ Utility_Behemoth(data = data, var = .x,
 myfactor = "infant_sex", normality = "dagostino", shape_palette = shape_sex,
  fill_palette = fill_sex, cex = 2, size = 3, corral.width = 1, statsHeight=NULL, scalePercent = TRUE, correction = "BH"))

Plot <- ThePlot[[1]] + labs(y = NULL, title = NULL) +
     theme(plot.caption = element_blank(),
      axis.text.y = element_text(size = 15),
       axis.text.x= element_text(size = 15)) #+ lims(y=c(0,NA))

Plot

Abbreviation <- "_sex.png"
ThePlotName <- paste0(PlotName, Abbreviation)
TheFile <- file.path(StorageLocation, ThePlotName)

ggsave(filename = TheFile, Plot, dpi = 600, width = 4, height = 3)
```

```{r}
print("Goodbye")
```
